The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2018-10-05 article.tex
Finished next iteration

The expected number of mutations $m$ of a phylogeny 
\richel{
  I think 'expected number of mutations' would be more correct.
  Do you agree?
}
with crown age $T$ in fact is given by
\richel{
  above stood 'crown age -T'. 
  I feel that a crown age is a positive number,
  but I know you have had a good reason.
  Perhaps better would be to write something explicit like:
  t_now - t_crown = T.
  Looking forward for a better suggestion than mine :-)
}

@@

Since we cannot know $n_{BD}(t)$ before running simulations
we need to replace it with a proxy. 
For this reason we will use the average number of
species in time according to the BD model. 
It's well known that this is equal to \gio{insert proper citation}
\richel{
  I see you use angle bracket as a notation for the expected
  value. I usually see 'E(x)' as the expected value for 'x',
  and this is used at the beloved https://en.wikipedia.org/wiki/Expected_value.
  What are the reasons you prefer the notation with the angle brackets?  
}

>>>>

The expected number of mutations $m$ of a phylogeny 
\richel{
  I think 'expected number of mutations' would be more correct.
  Do you agree?
}
with crown age $T$ in fact is given by
\richel{
  above stood 'crown age -T'. 
  I feel that a crown age is a positive number,
  but I know you have had a good reason.
  Perhaps better would be to write something explicit like:
  t\_now - t\_crown = T.
  Looking forward for a better suggestion than mine :-)
}

@@

Since we cannot know $n_{BD}(t)$ before running simulations
we need to replace it with a proxy. 
For this reason we will use the average number of
species in time according to the BD model. 
It's well known that this is equal to \gio{insert proper citation}
\richel{
  I see you use angle bracket as a notation for the expected
  value. I usually see 'E(x)' as the expected value for 'x',
  and this is used at the beloved https://en.wikipedia.org/wiki/Expected\_value.
  What are the reasons you prefer the notation with the angle brackets?  
}
